\section{Welcome to the TinyMCE editor demo!}
Meet \textbf{TinyMCE}, the Internet's most battle-tested rich text editor with
over 60 features including: \textit{Advanced formatting}, \textbf{\textit{Export
to and from Word and PDF}}, Accessibility and spelling checkers, Mentions and
comments, and \textbf{an AI assistant}.\par TinyMCE is easy to implement and
configure. \href{https://www.tiny.cloud/auth/signup/}{Try it out yourself today}.\par
\subsection{Popular features}
\begin{itemize}
	\item Collaborate with \href{https://www.tiny.cloud/docs/tinymce/latest/mentions/}{@Mentions},
		\href{https://www.tiny.cloud/docs/tinymce/latest/comments/}{discuss using
		Comments}
		and review changes.

	\item \href{https://www.tiny.cloud/docs/tinymce/latest/powerpaste/}{Paste from
		MS Word} and retain formatting.

	\item Power your email editor with \href{https://www.tiny.cloud/docs/tinymce/latest/mergetags/}{Merge
		tags}.
\end{itemize}
\subsection{Get TinyMCE}
\begin{tabular}{lll}
	\multicolumn{3}{l}{\textbf{TinyMCE meets all your architecture requirements.}} \\
	\textbf{Cloud}                                                                & \href{https://www.tiny.cloud/auth/signup/}{Sign-up for free} & Always up to date, easy to maintain \\
	\textbf{Self-hosted}                                                          & \href{https://www.tiny.cloud/pricing/}{Let's talk}           & With enterprise level support       \\
	\textbf{Open source}                                                          & \href{https://github.com/tinymce/tinymce}{Download today}    & Available under the GPLv2+ license  \\
\end{tabular}
\subsection{Why TinyMCE}
\begin{enumerate}
	\item \textbf{Out-of-the-box features save dev time.} From tables and spell
		checking to full collaboration.

	\item \textbf{Built to scale with you.} TinyMCE powers applications with
		millions of users.

	\item \textbf{Works where you build.} React, Vue, Angular, or vanilla JavaScript.

	\item \textbf{No one has been doing this longer.} 20+ years of stability and security.
\end{enumerate}
